Supercritical fluid extraction of essential oil from chamomile flowers: modelling, and parameter estimation

### 2024-04-08 SFE_article_Parameter_Estimation_short - Chamomile/Sections/Model.tex
08.04

	\subsubsection{Continuity equation} \label{CH: Continuity}
	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction ${\color{black}\phi}(z)$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}

	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$ to take into account the change of the cross-section available for the fluid. The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function ${\color{black}A_f}(z) = {\color{black}A\phi}(z)$. This modification accounts for the variability in the cross-sectional area available for fluid flow. Equation \ref{EQ: Continuity_differential} presents this adaptation in the differential form of the continuity equation, capturing the dynamics of the flow as it responds to changes in the cross-section.

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\phi}(z))}{\partial t} + \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z))}{\partial {\color{black}z}} = 0
		\end{equation}
	}
	where ${\color{black} A}$ is the total cross-section of the extractor and ${\color{black}\phi}(z)$ describe porosity along the extractor.

@@

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along ${\color{black}z}$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial ({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A \phi}(z) )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}={\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) v {\color{black}A\phi}(z)
		\end{equation}
	}

	To simplify the dynamics of the system, it is assumed that ${\color{black}F}={\color{black}F}(t)$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on ${\color{black}F}(t)$, ${\color{black}\phi}(z)$, and ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$.

	{\footnotesize
	\begin{equation}
		v = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}A\phi}(z)} 
	\end{equation}
	}

	The fluid density ${\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.

@@

	{\footnotesize
		\begin{equation}
			u = v {\color{black}\phi}(z) = \cfrac{{\color{black}F}(t)}{{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black} A} }
		\end{equation}
	}

@@

	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also predicated on the assumption that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, The mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase's behaviour accurately.

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial {\color{black}c_f}(t,z)}{\partial t}
			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial \left( {\color{black}c_f}(t,z) u\right)}{\partial {\color{black}z}}
			= \frac{1-{\color{black}\phi}(z)}{{\color{black}\phi}(z)} {\color{black}r_e}(t,z)
			+ \frac{1}{{\color{black}\phi}(z)} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial {\color{black}c_f}(t,z)}{\partial {\color{black}z}} \right)
		\end{equation}
	}

	${\color{black}c_f}(t,z)$ represents the concentration of solute in the fluid phase, , ${\color{black}r_e}(t,z)$ is a mass transfer kinetic term, and ${\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial diffusion coefficient.

@@

	{\footnotesize
		\begin{equation} 
			\label{Model_solid}
			%		{\scriptsize\begin{equation}
					\cfrac{\partial {\color{black}c_s}(t,z)}{\partial t} = \underbrace{ {\color{black}r_e}(t,z) }_{\text{Kinetics}}
			\end{equation} }

@@

%	As the solvent flows through the bed, the $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{black}c_s^*}$ and ${\color{black}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{black}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{Pf}}$ at the opening of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{black}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

	As the solvent flows through the bed, $CO_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions. The effect of Knudsen diffusion is negligible in this process, as the mean free path of the molecule is much smaller than the pore diameter. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{black}c_s^*}$ and ${\color{black}c_p^*}$, respectively, for solid and fluid phases. The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{black}c_{p}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{pf}}$ at the opening of the pore. The solute then diffuses through the film around the particle and reaches bulk concentration ${\color{black}c_f}$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined if the relationship between the solute concentration in one phase and its equilibrium concentration is known.

@@

			{\footnotesize
				\begin{equation} \label{Model_kinetic_basic}
					{\color{black}r_e}(t,z) = \cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - {\color{black}c_P^*}(t,z) \right)
			\end{equation} }

		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}({\color{black}T}(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).

		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase ${\color{black}c_s}(t,z)$

			{\footnotesize
				\begin{align} \label{Linear_equilibirum}
					{\color{black}c}(t,z) &= {\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
			\end{align} }

			The volumetric partition coefficient ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase. According to \citet{Spiro2007}, the term ${\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}({\color{black}T}(t,z))$.

			{\footnotesize
				\begin{align}
					{\color{black}k_m}({\color{black}T}(t,z)) = \cfrac{{\color{black}k_p}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}({\color{black}T}(t,z),{\color{black}P}(t))}
			\end{align} }

@@

			{\footnotesize
				\begin{equation}
					\label{Model_kinetic_no_sat}
					{\color{black}r_e}(t,z) = -\cfrac{{\color{black}D_i}({\color{black}T}(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left({\color{black}c_s}(t,z) - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}({\color{black}T}(t,z)){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))}   \right)
			\end{equation} }

@@

		\sout{The heat balance equation (equation  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance). Equation \ref{Model_heat} contains the convection and the diffusion terms. It is considered that there is no heat loss through the wall, and there is no heat generation in the system. The temperature of the extractor can be changed only by increasing the temperature of the inlet stream. The pseudo-homogenous phase is assumed to flow only in the axial direction. The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ because the solid phase is stationary. Therefore, this factor can be understood as the fraction of the fluid's total heat through convection. On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in Appendix. }

@@

			{\footnotesize
				\begin{equation} \label{Model_heat}
					\begin{split}
						\cfrac{\partial {\color{black}T}(t,z)}{\partial t} &= 
						\underbrace{ -\cfrac{{\color{black}F}(t) {\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon}){\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}C_p} ({\color{black}T}(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
						& + \underbrace{ {\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t)) \cfrac{\partial^2 {\color{black}T}(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
					\end{split}
			\end{equation} }

		where $ {\color{black}D^M_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial mass diffusion coefficient, ${\color{black}C_p}({\color{black}T}(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}F}(t))$ is the axial heat diffusion coefficient.

@@

			{\footnotesize
			\begin{align} \label{EQ: Heat_internal}
				&\cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}e}(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) A_f v {\color{black}e}(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right) 
			\end{align}
			}

@@

			{\footnotesize
				\begin{equation}
					d{\color{black}e}(t,z)=C_vd{\color{black}T}-\left[{\color{black}P}(t)-{\color{black}T}(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial {\color{black}T}(t,z)}\right)_{{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)
					\label{EQ: internal_energy_def}
				\end{equation} }

			where ${\color{black}e}^{id}(t,z)$ is the internal energy of perfect gas.

			Suppose a gas is considered to be perfectly caloric (${\color{black}e}(t,z)={\color{black}C_v} {\color{black}T}(t,z)$), then the energy equation can be written explicitly in the form of temperature. The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.

@@

			{\scriptsize
				\begin{equation}
					\begin{aligned}
					&\cfrac{{\color{black}e}(t,z)-{\color{black}e}^{id}(t,z)}{R{\color{black}T}(t,z)} = \\
					& - \cfrac{{\color{black}A}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left({\color{black}T}(t,z), {\color{black}P}(t)\right)} \right]
					\label{EQ: internal_energy_PR}
				\end{aligned}
			\end{equation}
			}

@@

			{\footnotesize
			\begin{equation}
				{\color{black}e}(t,z)={\color{black}e}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))=e( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) ) 
			\end{equation}
			}

			If the value of internal energy ${\color{black}e}(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed. A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}. Such a procedure allows to find a local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.

			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = {\color{black}e}(t,z) + {\color{black}P}(t) / {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t))$. By introducing the definition of enthalpy, the energy equation becomes

			{\footnotesize
				\begin{align} \label{EQ:Enthalpy_equation}
					\cfrac{\partial \left({\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial {\color{black}T}(t,z)}{\partial {\color{black}z}} \right)
				\end{align}
			}

@@

			{\footnotesize
				\begin{equation}
					{\color{black}h}(t,z)={\color{black}h}({\color{black}T}(t,z),{\color{black}P}(t),{\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)))={\color{black}h}( {\color{black}T}(t,z),{\color{black}P}(t), {\color{black}\rho_f}({\color{black}T}(t,z),{\color{black}P}(t)) ) 
					\label{EQ:Enthalpy_root}
				\end{equation}
			}

>>>>

	\subsubsection{Continuity equation} \label{CH: Continuity}
	 %When the cross-sectional area of the channel $A_f$ is specified as a function of the void fraction $\phi$ (where ${\color{black}\phi}$ is the void fraction of the bed and $A$ is the cross-section of the empty extractor), the continuity equation takes the form: %\todo[]{assign a color of v and u}

	%The obtained above quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is further modified by specifying a function $A_f = A\phi$ to take into account the change of the cross-section available for the fluid. The Equation \ref{EQ: Continuity_differential} shows the differential form of the continuity equation:

	The previously derived quasi-one-dimensional continuity equation (Equation \ref{EQ: CompressibleEuler_1}) is refined by incorporating a function $A_f = A\phi$. This modification accounts for the variability in the cross-sectional area available for fluid flow. Equation \ref{EQ: Continuity_differential} presents this adaptation in the differential form of the continuity equation, capturing the dynamics of the flow as it responds to changes in the cross-section.

	{\footnotesize
		\begin{equation} \label{EQ: Continuity_differential}
			\frac{\partial (\rho_f \phi)}{\partial t} + \frac{\partial (\rho_f v A\phi)}{\partial {\color{black}z}} = 0
		\end{equation}
	}
	where ${\color{black} A}$ is the total cross-section of the extractor and $\phi$ describe porosity along the extractor.

@@

	Assuming that the mass flow rate is constant in time, the temporal derivative becomes the mass flux F, and the spatial derivative can be integrated along $z$ as

	{\footnotesize
		\begin{equation}
			\int \frac{\partial (\rho_f v A \phi )}{\partial {\color{black}z}} dz = F \rightarrow {\color{black}F}=\rho_f v A\phi
		\end{equation}
	}

	To simplify the dynamics of the system, it is assumed that ${\color{black}F}=F$ is a control variable and affects the whole system instantaneously. This assumption allows for finding the velocity profile that satisfies mass continuity based on $F$, $\phi$, and $\rho_f$.

	{\footnotesize
	\begin{equation}
		v = \cfrac{F}{\rho_f A\phi} 
	\end{equation}
	}

	The fluid density $\rho_f$ can be obtained from an equation of state (Appendix \ref{CH: EOS}) if temperature and the thermodynamic pressure (assumed ${\color{black}P}(t)$ to be constant along ${\color{black}z}$ due to the low-Mach number condition) are known. The variation in density may be caused by the fluid accumulation in the system (equivalent to pressure change), which occurs instantaneously along ${\color{black}z}$ or by a temperature change.

@@

	{\footnotesize
		\begin{equation}
			u = v \phi = \cfrac{F}{\rho_f {\color{black} A} }
		\end{equation}
	}

@@

	The comprehensive derivation of the mass balance equation for the fluid phase is detailed in Appendix \ref{CH: Gouverning equations}. This equation accounts for the movement of the pseudo-homogeneous fluid phase (Equation \ref{Model_fluid}), which is constrained to the axial direction due to the quasi-one-dimensional approach that considers changes in the void fraction. It is also assumed that the thermodynamic pressure remains constant throughout the device, as illustrated by Equation \ref{EQ: Pressure_Velocity}. The analysis further simplifies the flow dynamics by disregarding the boundary layer near the extractor's inner wall, leading to a uniform velocity profile across any cross-section perpendicular to the axial direction. Given that the solute concentration in the solvent is negligible, the fluid phase is described as pseudo-homogeneous, with properties identical to the solvent itself. Thus, the mass balance equation encompasses convection, diffusion, and kinetic terms to represent the fluid phase behaviour accurately.

	{\footnotesize
		\begin{equation}
			\label{Model_fluid}
			\frac{\partial c_f}{\partial t}
			+ \frac{1}{\phi} \frac{\partial \left( c_f u\right)}{\partial {\color{black}z}}
			= \frac{1-\phi}{\phi} r_e
			+ \frac{1}{\phi} \frac{\partial}{\partial {\color{black}z}} \left( {\color{black}D^M_e} \frac{\partial c_f}{\partial {\color{black}z}} \right)
		\end{equation}
	}

	$c_f$ represents the concentration of solute in the fluid phase, , $r_e$ is a mass transfer kinetic term, and ${\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial diffusion coefficient.

@@

	{\footnotesize
		\begin{equation} 
			\label{Model_solid}
			%		{\scriptsize\begin{equation}
					\cfrac{\partial c_s}{\partial t} = \underbrace{ r_e }_{\text{Kinetics}}
			\end{equation} }

@@

%	As the solvent flows through the bed, the CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles through the solvent–solid matrix interactions. Assuming that the mean free path of the molecule is much smaller than the pore diameter, the effect of Knudsen diffusion is small and can be neglected. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. The graphical representation of the mass transfer mechanism is shown in Figure \ref{fig: SFE_Mechanism}. The mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$. At the solid-fluid interface, the equilibrium concentrations are given as ${\color{black}c_s^*}$ and ${\color{black}c_P^*}$, respectively for solid and fluid phases. The concentration of the solutes in the fluid phase in the centre of the pore is denoted as ${\color{black}c_{P}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{Pf}}$ at the opening of the pore. The solute diffuses through the film around the particle and reaches a concentration in the bulk ${\color{black}c_f}$. It can be assumed that the two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be introduced if the relation between the solute concentration in one phase and its equilibrium concentration is known.

	As the solvent flows through the bed, CO$_2$ molecules diffuse into the pores and adsorb on the particle surface to form an external fluid film around the solid particles due to the solvent-solid matrix interactions. The dissolved solute diffuses from the particle's core through the solid-fluid interface, the pore, and the film into the bulk. Figure \ref{fig: SFE_Mechanism} illustrates the mass transfer mechanism, where the mean solute concentration in the solid phase is denoted as ${\color{black}c_s}$ and the equilibrium concentrations at the solid-fluid interface are denoted as ${\color{black}c_s^*}$ and ${\color{black}c_p^*}$, respectively, for solid and fluid phases. The concentration of the solutes in the fluid phase in the center of the pore is denoted as ${\color{black}c_{p}}$. As the solute diffuses through the pore, its concentration changes and reaches ${\color{black}c_{pf}}$ at the opening of the pore. The solute then diffuses through the film around the particle and reaches bulk concentration ${\color{black}c_f}$. The two-film theory describes the solid-fluid interface inside the pore. The overall mass transfer coefficient can be determined if the relationship between the solute concentration in one phase and its equilibrium concentration is known.

@@

			{\footnotesize
				\begin{equation} \label{Model_kinetic_basic}
					r_e = \cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - {\color{black}c_P^*}(t,z) \right)
			\end{equation} }

		where ${\color{black}\mu}$ is sphericity, ${\color{black}l}$ a characteristic dimension of particles and can be defined as ${\color{black}l} = {\color{black}r}/3$, ${\color{black}r}$ is the mean particle radius, ${\color{black}\rho_s}$ is the solid density, ${\color{black}D_i}(T(t,z))$ corresponds to the overall diffusion coefficient and ${\color{black}c_P^*}(t,z)$ is a concentration at the solid-fluid interface (which according to the internal resistance model is supposed to be at equilibrium with the fluid phase).

		According to \citet{Bulley1984}, a linear equilibrium relationship (equation  \ref{Linear_equilibirum}) can be used to find an equilibrium concentration of the solute in the fluid phase ${\color{black}c_f^*}(t,z)$ is based on the concentration of the solute in the solid phase $c_s$

			{\footnotesize
				\begin{align} \label{Linear_equilibirum}
					{\color{black}c}(t,z) &= {\color{black}k_p}(T(t,z),{\color{black}P}(t)) \allowbreak {\color{black}q^*}(t,z)
			\end{align} }

			The volumetric partition coefficient ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ behaves as an equilibrium constant between the solute concentration in one phase and the corresponding equilibrium concentration at the solid-fluid interphase. According to \citet{Spiro2007}, the term ${\color{black}k_p}(T(t,z),{\color{black}P}(t))$ can be expressed as the function of mass partition factor ${\color{black}k_m}(T(t,z))$.

			{\footnotesize
				\begin{align}
					{\color{black}k_m}(T(t,z)) = \cfrac{{\color{black}k_p}(T(t,z),{\color{black}P}(t)) {\color{black}\rho_s}}{{\color{black}\rho}(T(t,z),{\color{black}P}(t))}
			\end{align} }

@@

			{\footnotesize
				\begin{equation}
					\label{Model_kinetic_no_sat}
					r_e = -\cfrac{{\color{black}D_i}(T(t,z), {\color{black}P}(t), F(t))}{{\color{black} \mu l^2} }\left(c_s - \cfrac{{\color{black}\rho_s}c_f(t,z)}{{\color{black}k_m}(T(t,z))\rho_f}   \right)
			\end{equation} }

@@

		\sout{The heat balance equation (equation  \ref{Model_heat}) was developed, assuming the existence of a pseudo-homogeneous phase, which properties are the mean between fluid and solid phases (the amount of solute is considered small enough not to affect the overall heat balance). Equation \ref{Model_heat} contains the convection and the diffusion terms. It is considered that there is no heat loss through the wall, and there is no heat generation in the system. The temperature of the extractor can be changed only by increasing the temperature of the inlet stream. The pseudo-homogenous phase is assumed to flow only in the axial direction. The numerator of the factor in front of the convection term of the heat equation contains only the specific heat of the fluid ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ because the solid phase is stationary. Therefore, this factor can be understood as the fraction of the fluid's total heat through convection. On the other hand, the axial heat diffusion is calculated based on the definition of thermal diffusivity for the fluid, as explained in Appendix. }

@@

			{\footnotesize
				\begin{equation} \label{Model_heat}
					\begin{split}
						\cfrac{\partial T(t,z)}{\partial t} &= 
						\underbrace{ -\cfrac{F {\color{black}C_p}(T(t,z),{\color{black}P}(t))}{{\color{black}A} 	[(1-{\color{black}\epsilon})\rho_f {\color{black}C_p} (T(t,z),{\color{black}P}(t)) + {\color{black} \epsilon \rho_s C_{ps} } ]} \cfrac{\partial T(t,z)}{\partial {\color{black}z}}  }_{\text{Convection}} + \\
						& + \underbrace{ {\color{black}D^T_e}(T(t,z),{\color{black}P}(t)) \cfrac{\partial^2 T(t,z)}{\partial {\color{black}z^2}} }_{\text{Diffusion}}
					\end{split}
			\end{equation} }

		where $ {\color{black}D^M_e}(T(t,z),{\color{black}P}(t),F)$ is the axial mass diffusion coefficient, ${\color{black}C_p}(T(t,z),{\color{black}P}(t))$ is the fluid's specific heat, ${\color{black}C_{ps}}$ is the specific heat of the solid phase, ${\color{black}D^T_e}(T(t,z),{\color{black}P}(t),F)$ is the axial heat diffusion coefficient.

@@

			{\footnotesize
			\begin{align} \label{EQ: Heat_internal}
				&\cfrac{\partial \left( \rho_f e(t,z) A_f \right) }{\partial t} + \cfrac{\partial \left( \rho_f A_f v e(t,z) \right)}{\partial {\color{black}z}} \nonumber \\
				&= -{\color{black}P}(t)\cfrac{\left( A_f v \right)}{\partial {\color{black}z}} + \cfrac{\partial}{\partial {\color{black}z}} \left( \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right) 
			\end{align}
			}

@@

			{\footnotesize
				\begin{equation}
					de(t,z)=C_vdT-\left[{\color{black}P}(t)-T(t,z)\left(\cfrac{\partial {\color{black}P}(t)}{\partial T(t,z)}\right)_{{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)}\right]d{\color{black}v_m}\left(T(t,z), {\color{black}P}(t)\right)
					\label{EQ: internal_energy_def}
				\end{equation} }

			where $e^{id}(t,z)$ is the internal energy of perfect gas.

			Suppose a gas is considered to be perfectly caloric ($e(t,z)={\color{black}C_v} T(t,z)$), then the energy equation can be written explicitly in the form of temperature. The perfectly caloric gas can be seen as the special case of a real gas, where the second term of Equation \ref{EQ: internal_energy_def} goes to zero and the heat capacity ${\color{black}C_v}$ is constant.

@@

			{\scriptsize
				\begin{equation}
					\begin{aligned}
					&\cfrac{e(t,z)-e^{id}(t,z)}{RT(t,z)} = \\
					& - \cfrac{{\color{black}A}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)\sqrt{8}} \cfrac{{\color{black}\kappa} \sqrt{\color{black}T_r}}{\sqrt{\alpha}} \ln \left[ \cfrac{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1+\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)}{{\color{black}Z}\left(T(t,z), {\color{black}P}(t)\right)+\left( 1-\sqrt{2} \right){\color{black}B}\left(T(t,z), {\color{black}P}(t)\right)} \right]
					\label{EQ: internal_energy_PR}
				\end{aligned}
			\end{equation}
			}

@@

			{\footnotesize
			\begin{equation}
				e(t,z)=e(T(t,z),{\color{black}P}(t),\rho_f)=e( T(t,z),{\color{black}P}(t), \rho_f ) 
			\end{equation}
			}

			If the value of internal energy $e(t,z)$ is known from the time evolution of the energy Equation \ref{EQ: CompressibleEuler_3}, and pressure is known from measurement, then the temperature can be reconstructed. A roootfinder can be used to find a value of temperature, which minimizes the difference between the value of internal energy coming from the time evolution (Equation \ref{EQ: Heat_internal}) and the output from Equation \ref{EQ: internal_energy_PR}. Such a procedure allows to find a local temperature along spatial direction ${\color{black}z}$ and needs to be repeated every time-step.

			Another way to express the energy equation is to introduce enthalpy ${\color{black}h}(t,z) = e(t,z) + {\color{black}P}(t) / \rho_f$. By introducing the definition of enthalpy, the energy equation becomes

			{\footnotesize
				\begin{align} \label{EQ:Enthalpy_equation}
					\cfrac{\partial \left(\rho_f {\color{black}h}(t,z) A_f\right)}{\partial t} &= - \cfrac{\partial \left( \rho_f {\color{black}h}(t,z) A_f v \right)}{\partial {\color{black}z}}  \nonumber \\
					& + \cfrac{\partial \left({\color{black}P}(t) A_f\right)}{\partial t} + \cfrac{\partial}{\partial {\color{black}z}} \left( k \cfrac{\partial T(t,z)}{\partial {\color{black}z}} \right)
				\end{align}
			}

@@

			{\footnotesize
				\begin{equation}
					{\color{black}h}(t,z)={\color{black}h}(T(t,z),{\color{black}P}(t),\rho_f)={\color{black}h}( T(t,z),{\color{black}P}(t), \rho_f ) 
					\label{EQ:Enthalpy_root}
				\end{equation}
			}
